Counting infinitely by oritatami co-transcriptional folding

### 2019-08-30 paper.tex
finised 8/30

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/rna_origami.pdf}
\caption{RNA origami}
\label{fig:rna_origami}
\end{figure}

@@

An \textit{oritatami system} (OS) $\Xi$ is a tuple $(\Sigma, R, \delta, \alpha, \sigma, w)$, where $\Sigma$ and $R$ are defined as above, while
\begin{itemize}
\item a positive integer $\delta$ called \textit{delay}, 
\item a positive integer $\alpha$ called \textit{arity}, %←arityの行だけ要らない？
\item an initial $R$-valid conformation $\sigma \in C_{\le \alpha}(\Sigma)$ called the \textit{seed},
\item a (possibly infinite) \textit{transcript} $w \in \Sigma^* \cup \Sigma^\omega$, which is to be folded upon the seed by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads. 
\end{itemize}
%
The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if 
\begin{equation}\label{eq:OS_CF}
C_{i+1} \in \argmin_{
\substack{
C \in \mathcal{C}_{\le \alpha} s.t. \\
C_i \xrightarrow{R}_{w[i+1]}C \\
}
}
\min \Bigl\{ \Delta G(C') \Bigm|
C \xrightarrow{R}^*_{w[i+2...i+k]}C', k\le \delta, C' \in \mathcal{C}_{\le \alpha}
\Bigr\}.
\end{equation}
%
Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
The easiest way to understand this stabilization process should be the video available at \href{https://www.dailymotion.com/video/x3cdj35}{\tt https://www.dailymotion.com/video/x3cdj35}, in which the Turing universal oritatami system by Geary et al. \cite{GeMeScSe2018}, whose delay is 3, is running. 
Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. %←
A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
%The oritatami system $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
%A deterministic oritatami system folds into a unique terminal conformation. 
%An oritatami system with the empty rule set just folds into an arbitrary elongation of its seed nondeterministically. 
%Thus, the rule set is reasonably assumed non-empty.

@@

@@

The transcript of our counter is periodic.
Its period \texttt{1}-\texttt{2}-\texttt{3}- $\cdots$ -\texttt{132} is semantically divided into the following 4 subsequences, called \textit{modules}:
\begin{itemize}
\item \texttt{1}--\texttt{30}: Format module or F
\item \texttt{31}--\texttt{66}: Left-Turn module or L
\item \texttt{67}--\texttt{96}: Half-Adder module or H
\item \texttt{97}--\texttt{132}: Right-Turn module  or R
\end{itemize}
The transcript can be hence represented as $(FLHR)^*$ at the module level. Modules are to play their roles in expected environments by folding into respective conformations which should be pairwise-distinct enough to be distinguishable by other modules transcribed later.
Such expected conformations are called a \textit{brick}.
For example, module F encounters the four environments shown in Fig.~\ref{fig:formatters} where it takes the four bricks, respectively.
Here, by saying (an instance of) a module folds into (or takes) a brick in an environment, what we actually mean is that the rule set is designed so as for the transcript of the module to interact with itself as well as the environment into that brick according to the oritatami dynamics  \eqref{eq:OS_CF}.
The whole system is designed to guarantee that each module is transcribed only in one of the environments it expects.
This fact is illustrated in the \textit{brick automaton} in Fig.~\ref{fig:brickautomaton}, which describes pairs of an environment and a brick and transitions between them.
Since this automaton is closed, it suffices to test whether for all pairs of an environment and a brick, the brick is folded in the environment.
This test has been done using our simulator developed for this project.
All the certificates can be found at \href{https://komaruyama.github.io/oritatami-infinit-counter/}{\texttt{https://komaruyama.github.io/oritatami-infinit-counter/}}.

@@

 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.8\linewidth]{fig/svg/Rb_1.pdf}

@@

 \end{tabular}
 \caption{All the three bricks of module R: \texttt{Rt}, \texttt{Rb}, and \texttt{Rcr}.
 In zigs, R folds into \texttt{Rt} or \texttt{Rb}.
 In zags, R always folds into \texttt{Rb} until the transcript reaches the right end, where R folds into \texttt{Rcr}.}
 \label{fig:rightturns}
\end{figure}

\paragraph{Seed and Encoding.}
The initial counter value is encoded as $b_{k-1}b_{k-2} \cdots b_1b_0$ in binary on the seed in the following format
\begin{equation} \label{eq:zagencoding}
\texttt{64}{-}\texttt{65}{-}\texttt{66}{-}\left( \prod^0_{i = k-1} \bigl(  w_{Hn} w_{Rb} w_{Fb_i} w_{Lbn} \bigr) \right) w_{Hn}
\end{equation}
where 
$w_{Hn}= \texttt{67}{-}\texttt{76}{-}\texttt{77}{-}\texttt{78}{-}\texttt{79}{-}\texttt{88}{-}\texttt{89}{-}\texttt{90}{-}\texttt{91}{-}\texttt{96}$, 
$w_{Rb}=\texttt{97}{-}\texttt{102}{-}\texttt{103}{-}\texttt{108}{-}$ $\texttt{109}{-}\texttt{114}{-}\texttt{115}{-}\texttt{120}{-}\texttt{121}{-}\texttt{126}{-}\texttt{127}{-}\texttt{132}$, 
$w_{F0} = \texttt{1}{-}\texttt{10}{-}\texttt{11}{-}\texttt{12}{-}\texttt{13}{-}\texttt{22}{-}\texttt{23}{-}\texttt{24}{-}$ $\texttt{25}{-}\texttt{30}$, 
$w_{F1}=\texttt{1}{-}\texttt{22}{-}\texttt{23}{-}\texttt{24}{-}\texttt{25}{-}\texttt{26}{-}\texttt{27}{-}\texttt{28}{-}\texttt{29}{-}\texttt{30}$, 
$w_{Lbn}= \texttt{31}{-}\texttt{36}{-}\texttt{37}{-}\texttt{42}{-}$ $\texttt{43}{-}\texttt{48}{-}\texttt{49}{-}\texttt{54}{-}\texttt{55}{-}\texttt{64}{-}\texttt{65}{-}\texttt{66}$
are sequences of bead types exposed downward by modules H, R, F, L when they fold into bricks \texttt{Hn}, \texttt{Rb}, \texttt{F}$b_i$, \texttt{Lbn}, respectively, which can be found in Figs.~\ref{fig:halfadders}, \ref{fig:rightturns}, \ref{fig:formatters}, and \ref{fig:leftturns}.
For instance, the seed for $k = 1$ and $b_0 = 0$ is colored in purple in Fig.~\ref{fig:counter1stzig}.
%$w_{Hn} = 67{-}76{-}77{-}78{-}79{-}88{-}89{-}90{-}91{-}96$ \\
%$w_{Rb} = 97{-}102{-}103{-}108{-}109{-}114{-}115{-}120{-}121{-}126{-}127{-}132$\\
%$w_{Lbn} = 31{-}36{-}37{-}42{-}43{-}48{-}49{-}54{-}55{-}64{-}65{-}66$

\subsection{Brick level overview}
Starting from the seed, this system cyclically transits four phases: zig ($\leftarrow$), left carriage-return ($\hookrightarrow$), zag ($\rightarrow$), and right carriage-return ($\hookleftarrow$). 
The prefix $(FLHR)^k F$ of the transcript folds into the first zig (recall that $k$ is the bit-width of the initial value). 
In zigs in general, all the instances of modules F and H fold into bricks of width 10 and height 3, while all the instances of  L and R fold into bricks of width 12 and height 3. 
Zigs thus turn out to be a linear structure of height 3. 
In the process of the prefix folding into the first zig, its $i$-th instance of $H$ is transcribed right below $b_{i-1}$ encoded on the seed in the format (2) so that the H can ``read" $b_{i-1}$. 
After the whole prefix thus has folded into the first zig, the next L is transcribed right below Turn Signal, which lets the L fold into a special brick for left carriage-return if the zig ended at the top (this occurs when $b_{k-1} b_{k-2} \cdots b_0 < 1^k$) (see Fig.~\ref{fig:counter1stzag}). 
We should note that this special brick \texttt{Lcre} is provided with another Turn Signal for the sake of next left carriage-return.
Having been thus carriage-returned, the succeeding subsequence $(HRFL)^k H$ of the transcript folds into the first zag.
Even in zags instances of F and H fold into bricks of width 10 and height 3, while those of L and R fold into bricks of width 12 and height 3. 
As a result, zags turn out to be a linear structure of height 3. 
More importantly, instances of H and F are aligned vertically and alternately into columns (see Figs.~\ref{fig:counter1stzig}-\ref{fig:overflowex1}), $i$-th of which from the right propagates the ($i{-}1$)-th bit of the counter value downward. 
After the whole subsequence has folded into the first zag, an instance of $R$ is transcribed and folded into a special brick \texttt{Rcr} for carriage-return due to the turn signal \texttt{125}-\texttt{124}-\texttt{123}-\texttt{122}, which occurs also at the bottom of \texttt{Rcr} for the sake of next right carriage-return. 
This amounts to one cycle of the phase transition.

@@

In a zig, module H plays its primary role as half-adder and carry transfers through instances of others (F, L, and R) from an instance of H to another for more significant bit.
Carry is transferred as a height for modules to start.
In zigs, modules F, L, and R take respective two bricks (\texttt{Fnt} and \texttt{Fnb} for F, \texttt{Lt} and \texttt{Lbn} for L, and \texttt{Rt} and \texttt{Rb} for R; see Fig.~\ref{fig:formatters}, \ref{fig:leftturns}, and \ref{fig:rightturns}) both of which start and end at the same height: one at the top while the other at the bottom.
A zig is fed with carry by being forced to start at the bottom by the last \texttt{Rcr} or the seed.
Until the count overflows, module H encounters only four environments, which encode input 0 as $w_{F0}$ or 1 as $w_{F1}$ and carry or no-carry as of whether the module starts at the bottom or top, where it takes \texttt{H00}, \texttt{H01}, \texttt{H10}, and \texttt{H11}, respectively, as shown in Fig.~\ref{fig:halfadders} (\texttt{H}$xc$ is folded when the input is $x$ and the carry is given if $c=1$ or not otherwise).

@@

Let us see how the subsequence $(FLHR)^kF$ folds into a zig; for $k=1$ and the current value 0, see Fig.~\ref{fig:counter1stzig}.
The zig is initially fed with carry by being forced to start folding at the bottom and the carry is propagated through the first instances of F and L in the way just explained toward the first instance of H.
This H is thus fed with carry and folds into \texttt{H01} if the bit encoded above is 0, as illustrated in Fig.~\ref{fig:counter1stzig}, or \texttt{H11} if the bit is rather 1.
\texttt{H01} ends at the top, corresponding to no-carry.
This absence of carry propagates through the succeeding modules leftward.
As a result, the zig ends, or more precisely an instance of F ends folding at the bottom if the current value is overflowed (Fig.~\ref{fig:overflowex1}), or at the top otherwise. (Fig.~\ref{fig:counter1stzig}).
An instance of L is to be transcribed next.
It folds either into \texttt{Lcrn} for (normal) carriage-return unless the current value is overflowed, or into \texttt{Lbe} at an overflow.

\subsubsection{In the zag ($\rightarrow$)}
Here, the value incremented in the previous zig is formatted so as to be exposed below in the format \eqref{eq:zagencoding} for the next zig.
A subsequence $(HRFL)^kH$ of the transcript folds into the zag, where $k$ is the bit width of the incremented value.
Both of the bricks of L for carriage-return, i.e., \texttt{Lcrn} and \texttt{Lcre}, ends at the bottom so that zags start at the bottom.
The first instances of H and R fold into \texttt{Hn} and \texttt{Rb}, respectively.
Hence, the next F starts at the bottom and takes the brick \texttt{F}$y$ under the module H  that takes the brick \texttt{H}$xc$ in the previous zig, where $y$ is the output of the module, that is, $y = (x+c) \mod 2$.
Both of these bricks \texttt{F0} and \texttt{F1} end at the bottom so that the instance of L folds into \texttt{Lbn}.

@@

% Lbeの後の話 Lcreまで
In the case of overflow, instance of H,  R, and F are transcribed following \texttt{Lbc} and they fold into \texttt{He1}, \texttt{Rb}, and \texttt{Fnb}, respectively.
Next instance of L which is transcribed after \texttt{Fnb} carriage-return for the next zag.
However, if its instance turn, Turn Signal must be present around there so the top of \texttt{Fnb} is given the role of Turn Signal.
Unless the count overflows, there is a brick above \texttt{Fnb} as shown in Fig.~\ref{fig:overflowex1}, so the top of \texttt{Fnb} is hidden, but when it overflows, Turn Signal is exposed.

Module H read from the row above the value encoded into folding in the module F during the previous zag-phase, and fold into a shape H00, H10, H01, H11.
H$xc$ is corresponding to the case where $x$ is the bit read in the row above and $c$ is the carry. 
In the zig pass module R, F, and L just propagate the carry value to the next.

When the zig pass reaches the left most part, module L collaborates with above turn module and it is folded turn module which reverses the folding direction for next zag pass except carry = 1.
At this time, if module L has a carry, folding of module L is glider and it go straight in order to expand bit width after that next module L turns to zag pass while folding turn module.
%H -> He1

\subsubsection{In the zag ($\rightarrow$)}
This part, instances of module F copy the current value, which incremented in the previous zig and encoded at below the zig.
Module F is always folded under module H in zags and F takes the two bricks F0 and F1 shown in Fig.~\ref{fig:formatters} which depending on a brick of module H.
Other modules H,R, and L take bricks which do nothing Hn, Rb, and Lbc, respectively, shown in Fig.~\ref{fig:halfadders}, \ref{fig:rightturns}, \ref{fig:leftturns}.

a

Module F read form the row above H$xc$, and fold into a shape F0, F1.
F$y$ is corresponding to the case where $y = (x + c)$ mod $2$.
There are no carry propagation and the module L, H, R fold into Lbc, Hn, Rb in this pass.

When the zag pass reaches the right most part. module R collaborates with above turn module and it is folded turn module which reverses the folding direction for next zag pass.

\subsection{Example of folding first zigzag}
Let's run an infinite counter from 1 bit width.
The seed is encoded with "0", and the starts from bottom row, that is, giving a carry for the least significant bit.

\subsubsection{The first zig pass ($\leftarrow$)}
In Fig,~\ref{fig:counter1stzig}, the zig pass folds as follows.
\begin{itemize}
\item{[First module F (Light Green)]} \\Normally, module H is folded above module F, and the seed corresponding to this module H now represents None.
Then, module F forms a shape which represents None and propagates carry equal to 1.
\item{[First module L (Light Blue)]} \\Since the seed here does not have a turn signal, module L forms glider and propagates carry while extending straight.

\item{[First module H (Pink)]} \\The seed is encoded 0 and module folding starts from the bottom row, that is, the carry equal to 1.
Then, HA folds into H01, which represents 1 and is output of carry equal 0.

\item{[First module R (Yellow) and 2nd module F]} \\Both module form glider which start from top row and end to top row, in order to propagate carry equal 0.

\end{itemize}

\subsubsection{The first zag pass ($\rightarrow$)}
In Fig. \ref{fig:counter1stzig}, it is folded until second module F, and module L is transferred as the next transcript.
Fig. \ref{fig:counter1stzag} shows how zag pass is folded.
Now, there is a Turn Signal at the left end of the seed, so L's transcript binds to its signal and loses the shape of glider in order to turn.
In addition, the turned module L forms a Turn Signal at its end.

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/rna_origami.pdf}
\caption{RNA origami. RNA polymerase enzyme (orange) synthesizes the temporal copy (blue) of a gene (gray spiral) out of ribonucleotides of four types A, C, G, and U.}
\label{fig:rna_origami}
\end{figure}

@@

An \textit{oritatami system} (OS) $\Xi$ is a tuple $(\Sigma, R, \delta, \alpha, \sigma, w)$, where $\Sigma$ and $R$ are defined as above, while the other elements are
\begin{itemize}
\item a positive integer $\delta$ called \textit{delay}, 
\item a positive integer $\alpha$ called \textit{arity}, %←arityの行だけ要らない？
\item an initial $R$-valid conformation $\sigma \in C_{\le \alpha}(\Sigma)$ called the \textit{seed},
\item a (possibly infinite) \textit{transcript} $w \in \Sigma^* \cup \Sigma^\omega$, which is to be folded upon the seed by stabilizing beads of $w$ one at a time so as to minimize energy collaboratively with the succeeding $\delta{-}1$ nascent beads. 
\end{itemize}
%
The energy of a conformation $C = (P, w, H)$, denoted by $\Delta G(C)$, is defined to be ${-}|H|$; the more bonds a conformation has, the more stable it gets. 
The set $\mathcal{F}(\Xi)$ of conformations \textit{foldable} by the system $\Xi$ is recursively defined as: the seed $\sigma$ is in $\mathcal{F}(\Xi)$; and provided that an elongation $C_i$ of $\sigma$ by the prefix $w[1..i]$ be foldable (i.e., $C_0 = \sigma$), its further elongation $C_{i+1}$ by the next bead $w[i+1]$ is foldable if 
\begin{equation}\label{eq:OS_CF}
C_{i+1} \in \argmin_{
\substack{
C \in \mathcal{C}_{\le \alpha} s.t. \\
C_i \xrightarrow{R}_{w[i+1]}C \\
}
}
\min \Bigl\{ \Delta G(C') \Bigm|
C \xrightarrow{R}^*_{w[i+2...i+k]}C', k\le \delta, C' \in \mathcal{C}_{\le \alpha}
\Bigr\}.
\end{equation}
%
Then we say that the bead $w[i+1]$ and the bonds it forms are \textit{stabilized} according to $C_{i+1}$. 
The easiest way to understand this stabilization process should be the video available at \href{https://www.dailymotion.com/video/x3cdj35}{\tt https://www.dailymotion.com/video/x3cdj35}, in which the Turing universal oritatami system by Geary et al. \cite{GeMeScSe2018}, whose delay is 3, is running. 
Note that an arity-$\alpha$ oritatami system cannot fold any conformation of arity larger than $\alpha$. %←
A conformation foldable by $\Xi$ is \textit{terminal} if none of its elongations is foldable by $\Xi$. 
%The oritatami system $\Xi$ is \textit{deterministic} if for all $i \ge 0$, there exists at most one $C_{i+1}$ that satisfies \eqref{eq:OS_CF}. 
%A deterministic oritatami system folds into a unique terminal conformation. 
%An oritatami system with the empty rule set just folds into an arbitrary elongation of its seed nondeterministically. 
%Thus, the rule set is reasonably assumed non-empty.

@@

%%

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{fig/svg/inf-ai_c_2.pdf}
\vspace*{5mm}

	\node[below, shift=(-90:1)] at (ho) {h};
	\node[below, shift=(-90:1)] at (ka) {k};
	\node[below, shift=(-90:0.8)] at (ro) {r};
	\node[below, shift=(-90:0.8)] at (fa) {f};
	\node[below, shift=(-90:0.8)] at (ci) {c};
\end{tikzpicture}
}
\caption{The brick automaton of infinite binary counter}
\label{fig:brickautomaton}
\end{figure}

%%

@@

The transcript of our counter is periodic.
Its period \texttt{1}-\texttt{2}-\texttt{3}- $\cdots$ -\texttt{132} is semantically divided into the following 4 subsequences, called \textit{modules}:
\begin{itemize}
\item \texttt{1}--\texttt{30}: Format module or F
\item \texttt{31}--\texttt{66}: Left-Turn module or L
\item \texttt{67}--\texttt{96}: Half-Adder module or H
\item \texttt{97}--\texttt{132}: Right-Turn module  or R
\end{itemize}
The transcript can be hence represented as $(FLHR)^*$ at the module level. Modules are to play their roles in expected environments by folding into respective conformations which should be pairwise-distinct enough to be distinguishable by other modules transcribed later.
Such expected conformations are called a \textit{brick}.
For example, module F encounters the four environments shown in Fig.~\ref{fig:formatters} where it takes the four bricks, respectively.
Here, by saying (an instance of) a module folds into (or takes) a brick in an environment, what we actually mean is that the rule set is designed so as for the transcript of the module to interact with itself as well as with the environment into that brick according to the oritatami dynamics  \eqref{eq:OS_CF}.
The whole system is designed to guarantee that each module is transcribed only in one of the environments it expects.
This fact is illustrated in the \textit{brick automaton} in Fig.~\ref{fig:brickautomaton}, which describes pairs of an environment and a brick as a vertex and transitions between them.
Since this automaton is closed, it suffices to test whether for all pairs of an environment and a brick, the brick is folded in the environment.
This test has been done using our simulator developed for this project.
All the certificates can be found at \href{https://komaruyama.github.io/oritatami-infinit-counter/}{\texttt{https://komaruyama.github.io/oritatami-infinit-counter/}}.

@@

 \begin{minipage}{0.5\linewidth}
  \centering
   \includegraphics[width=0.8\linewidth]{fig/svg/Rb_1(2).pdf}\\\ \\
   \includegraphics[width=0.8\linewidth]{fig/svg/Rb_1.pdf}

@@

 \end{tabular}
 \caption{All the three bricks of module R: \texttt{Rt}, \texttt{Rb}, and \texttt{Rcr}.
 In zigs, R folds into \texttt{Rt} or \texttt{Rb}, depending on how high it starts.
 In zags, R always folds into \texttt{Rb} until the transcript reaches the right end, where R folds into \texttt{Rcr}.}
 \label{fig:rightturns}
\end{figure}

\paragraph{Seed and Encoding.}
The initial counter value is encoded as $b_{k-1}b_{k-2} \cdots b_1b_0$ in binary on the seed in the following format
\begin{equation} \label{eq:zagencoding}
\texttt{64}{-}\texttt{65}{-}\texttt{66}{-}\left( \prod^0_{i = k-1} \bigl(  w_{Hn} w_{Rb} w_{Fb_i} w_{Lbn} \bigr) \right) w_{Hn}
\end{equation}
where 
\begin{eqnarray*}
w_{Hn} &=& \texttt{67}{-}\texttt{76}{-}\texttt{77}{-}\texttt{78}{-}\texttt{79}{-}\texttt{88}{-}\texttt{89}{-}\texttt{90}{-}\texttt{91}{-}\texttt{96},\\
w_{Rb} &=& \texttt{97}{-}\texttt{102}{-}\texttt{103}{-}\texttt{108}{-}\texttt{109}{-}\texttt{114}{-}\texttt{115}{-}\texttt{120}{-}\texttt{121}{-}\texttt{126}{-}\texttt{127}{-}\texttt{132},\\
w_{F0} &=& \texttt{1}{-}\texttt{10}{-}\texttt{11}{-}\texttt{12}{-}\texttt{13}{-}\texttt{22}{-}\texttt{23}{-}\texttt{24}{-}\texttt{25}{-}\texttt{30},\\
w_{F1} &=& \texttt{1}{-}\texttt{22}{-}\texttt{23}{-}\texttt{24}{-}\texttt{25}{-}\texttt{26}{-}\texttt{27}{-}\texttt{28}{-}\texttt{29}{-}\texttt{30},\\
 w_{Lbn} &=& \texttt{31}{-}\texttt{36}{-}\texttt{37}{-}\texttt{42}{-}\texttt{43}{-}\texttt{48}{-}\texttt{49}{-}\texttt{54}{-}\texttt{55}{-}\texttt{64}{-}\texttt{65}{-}\texttt{66}
\end{eqnarray*}
are sequences of bead types exposed downward by modules H, R, F, L when they fold into bricks \texttt{Hn}, \texttt{Rb}, \texttt{F}$b_i$, \texttt{Lbn}, respectively, which can be found in Figs.~\ref{fig:halfadders}, \ref{fig:rightturns}, \ref{fig:formatters}, and \ref{fig:leftturns}.
For instance, the seed for $k = 1$ and $b_0 = 0$ is colored in purple in Fig.~\ref{fig:counter1stzig}.
%$w_{Hn} = 67{-}76{-}77{-}78{-}79{-}88{-}89{-}90{-}91{-}96$ \\
%$w_{Rb} = 97{-}102{-}103{-}108{-}109{-}114{-}115{-}120{-}121{-}126{-}127{-}132$\\
%$w_{Lbn} = 31{-}36{-}37{-}42{-}43{-}48{-}49{-}54{-}55{-}64{-}65{-}66$

\subsection{Brick level overview}
Starting from the seed, this system cyclically transits four phases: zig ($\leftarrow$), left carriage-return ($\hookrightarrow$), zag ($\rightarrow$), and right carriage-return ($\hookleftarrow$). 
The prefix $(FLHR)^k F$ of the transcript folds into the first zig (recall that $k$ is the bit-width of the initial value). 
In zigs in general, all the instances of modules F and H fold into bricks of width 10 and height 3, while all the instances of  L and R fold into bricks of width 12 and height 3. 
Zigs thus turn out to be a linear structure of height 3. 
We can inductively observe that the $i$-th instance of H in the prefix is transcribed right below $b_{i-1}$ encoded on the seed in the format (2) so that the H can ``read" $b_{i-1}$. 
After the whole prefix thus has folded into the first zig, the next L is transcribed right below Turn Signal, which lets the L fold into a special brick for left carriage-return if the zig ended at the top (this occurs when $b_{k-1} b_{k-2} \cdots b_0 < 1^k$) (see Fig.~\ref{fig:counter1stzag}). 
We should note that this special brick \texttt{Lcre} is provided with another Turn Signal for the sake of next left carriage-return.
Having been thus carriage-returned, the succeeding subsequence $(HRFL)^k H$ of the transcript folds into the first zag.
Even in zags instances of F and H fold into bricks of width 10 and height 3, while those of L and R fold into bricks of width 12 and height 3. 
As a result, zags turn out to be a linear structure of height 3. 
More importantly, instances of H and F are aligned vertically and alternately into columns (see Figs.~\ref{fig:counter1stzig}-\ref{fig:overflowex1}), $i$-th of which from the right propagates the ($i{-}1$)-th bit of the counter value downward. 
After the whole subsequence has folded into the first zag, an instance of $R$ is transcribed and folded into a special brick \texttt{Rcr} for carriage-return due to the turn signal \texttt{125}-\texttt{124}-\texttt{123}-\texttt{122}, which occurs also at the bottom of \texttt{Rcr} for the sake of next right carriage-return. 
This amounts to one cycle of the phase transition.

@@

In a zig, module H plays its primary role as a half-adder and carry transfers through instances of others (F, L, and R) from an instance of H to another for more significant bit.
Carry is transferred as a height for modules to start.
In zigs, modules F, L, and R take the respective two bricks (\texttt{Fnt} and \texttt{Fnb} for F, \texttt{Lt} and \texttt{Lbn} for L, and \texttt{Rt} and \texttt{Rb} for R; see Figs.~\ref{fig:formatters}, \ref{fig:leftturns}, and \ref{fig:rightturns}), both of which start and end at the same height: one at the top while the other at the bottom.
A zig is carried by being forced to start at the bottom by the last \texttt{Rcr} or the seed.
Until the count overflows, module H encounters only four environments, which encode input 0 as $w_{F0}$ or 1 as $w_{F1}$ and carry or no-carry as of whether the module starts at the bottom or top, where it takes \texttt{H00}, \texttt{H01}, \texttt{H10}, and \texttt{H11}, respectively, as shown in Fig.~\ref{fig:halfadders} (\texttt{H}$xc$ is folded when the input is $x$ and the carry is given if $c=1$ or not otherwise).

@@

Let us see how the subsequence $(FLHR)^kF$ folds into a zig; for $k=1$ and the current value 0, see Fig.~\ref{fig:counter1stzig}.
The zig starts at the bottom, that is, being carried and the carry is transferred through the first instances of F and L in the way just explained toward the first instance of H.
This H is thus fed with carry and folds into \texttt{H01} if the bit encoded above is 0, as illustrated in Fig.~\ref{fig:counter1stzig}, or \texttt{H11} if the bit is rather 1.
\texttt{H01} ends at the top, corresponding to canceling the carry out.
This absence of carry transfers through the succeeding modules leftward.
As a result, the zig ends, or more precisely an instance of F ends folding at the bottom if the current value is overflowed (Fig.~\ref{fig:overflowex1}), or at the top otherwise (Fig.~\ref{fig:counter1stzig}).
An instance of L is to be transcribed next.
It folds either into \texttt{Lcrn} for (normal) carriage-return unless the current value is overflowed, or into \texttt{Lbe} at an overflow.

\subsection{Bit width expansion at an overflow}

The counter of Geary et al. cannot handle a zig that ends at the bottom, that is, its behavior is undefined at an overflow.
In contrast, module L in this infinite counter is designed so as to fold into \texttt{Lbe} in this situation in order to continue counting up (Fig.~\ref{fig:overflowex2}).
Observe that the dent on Turn Signal made of \texttt{58}, \texttt{63}, and \texttt{64} is too far for module L or more precisely its beads \texttt{33} and \texttt{34} to interact with the dent strongly enough to fold into \texttt{Lcrn}.
\texttt{Lbe} is a self-sustaining conformation (glider) so that it can fold even if nothing is around, which occurs at that very moment.
For the same reason, the following instances of H, R, and F fold into self-sustaining conformations \texttt{He1}, \texttt{Rb}, and \texttt{Fnb}, respectively (Figs.~\ref{fig:overflowex3} and \ref{fig:overflowex4}).
%If the beads \texttt{33} and \texttt{34} bind to Turn Signal, module L folds into \texttt{Lcrn}, but now, these beads cannot reach to Turn Signal because module L is starting at the bottom.
Note that \texttt{He1} is essentially the same as \texttt{H00} but exposes the opposite side downward, which will be interpreted as the leading bit 1 after expansion in the next zag.
When the next instance of L is transcribed, there is nothing around.
Nevertheless, it does not fold into \texttt{Lbe} but folds into \texttt{Lcre} for carriage-return; how?
It is guided by interaction between the beads \texttt{35}, \texttt{36} along the transcript of L and the Turn Signal \texttt{28}{-}\texttt{27}{-}\texttt{22} above \texttt{Fnb} (Figs.~\ref{fig:leftturns}, \ref{fig:overflowex4}, and \ref{fig:overflowex5}).
This signal is usually hidden geometrically by the previous zag, and hence, does no harm.

\subsection{Formatting}
The value has been successfully incremented but it is not in the format \eqref{eq:zagencoding} yet.
In the upcoming zag, instances of F play their primary role to format 1 bit output by module H (recall that instances of H and F are aligned vertically and alternately).
Both of the bricks of L for carriage-return, i.e., \texttt{Lcrn} and \texttt{Lcre}, ends at the bottom so that zags start at the bottom.
All modules start and end at the bottom in zags; note that nothing has to be transferred between modules.
That is, instances of H, L, and R fold into \texttt{Hn}, \texttt{Lbn}, and \texttt{Rb}, respectively.
Below the brick \texttt{H}$xc$, an instance of F folds into \texttt{F}$y$, where $y = (x+c) \mod 2$.

%
%Here, the value incremented in the previous zig is formatted so as to be exposed below in the format \eqref{eq:zagencoding} for the next zig.
%A subsequence $(HRFL)^kH$ of the transcript folds into the zag, where $k$ is the bit width of the incremented value.
%Both of the bricks of L for carriage-return, i.e., \texttt{Lcrn} and \texttt{Lcre}, ends at the bottom so that zags start at the bottom.
%The first instances of H and R fold into \texttt{Hn} and \texttt{Rb}, respectively.
%Hence, the next F starts at the bottom and takes the brick \texttt{F}$y$ under the module H  that takes the brick \texttt{H}$xc$ in the previous zig, where $y$ is the output of the module, that is, $y = (x+c) \mod 2$.
%Both of these bricks \texttt{F0} and \texttt{F1} end at the bottom so that the instance of L folds into \texttt{Lbn}.

@@

\section{conclusion}

%\centering
%\begin{table}[tb]
%\begin{tabular}{c c c c}
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/bglider.pdf}}
%\end{minipage} &
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/tglider.pdf}}
%\end{minipage} &
%\begin{minipage}{30mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/plane.pdf}}
%\end{minipage} &
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/spiral.pdf}}
%\end{minipage}\\
%
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/horn.pdf}}
%\end{minipage} &
%\begin{minipage}{30mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/kar.pdf}}
%\end{minipage} &
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/roof.pdf}}
%\end{minipage}\\
%
%\begin{minipage}{25mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/fault.pdf}}
%\end{minipage} &
%\begin{minipage}{30mm}
%	\centering
%       \scalebox{0.5}{\includegraphics{fig/svg/cliff.pdf}}
%\end{minipage}\\
%
%\end{tabular}
%\end{table}

\bibliographystyle{splncs03}
\bibliography{sofsem2020}
